Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-14 manuscript/manuscript.tex
Fix grid table
Continue writing sinusoidal density subsection

\begin{table}
\caption{
    Description of the computation grids used to characterize the accuracy of the
    numerical integration.
    Grid height is defined above the mean Earth radius.
}
\label{tab:grids}
\begin{tabular}{lccc}
    Name & Grid size & Grid region (degrees) & Grid height (km)
    \\ \hline
    Pole      & $0.1^\circ \times 0.1^\circ$ & 0E / 1E / 89N / 90N  & 0   \\
    Equator   & $0.1^\circ \times 0.1^\circ$ & 0E / 1E / 0N  / 1N   & 0   \\
    Global    & $ 10^\circ \times  10^\circ$ & 0E / 1E / 0N  / 1N   & 0   \\
    Satellite & $ 10^\circ \times  10^\circ$ & 0E / 1E / 89N / 90N  & 260 \\
\end{tabular}
\end{table}

@@

\subsection{Trigonometric Density}

@@

We will consider spherical shells with a trigonometric density defined as follows:

\begin{equation}
    \rho(r') = A \sin \left( 2 \pi b \frac{r' - R}{T} \right) + A,
    \label{eq:sine-density}
\end{equation}

@@

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the $g_z$ of spherical shells with this kind of
sinusoidal density function.
The analytical solution for the potential $V$ can be found on Appendix~\ref{sec:shell}.
The gravitational fields are computed on every grid detailed in Table~\ref{tab:grids}
and making use of the spherical shells defined on Table~\ref{tab:shell-models}.
Each shell is assigned with different sinusoidal density functions by changing the
values of $b$ in Eq.~\ref{eq:sine-density} (Fig.~\ref{fig:sine-densities}).

>>>>

\begin{table}
\caption{
    Description of the computation grids used to characterize the accuracy of the
    numerical integration.
    Grid height is defined above the mean Earth radius.
}
\label{tab:grids}
\begin{tabular}{lccc}
    Name & Grid size & Grid region (degrees) & Grid height (km)
    \\ \hline
    Pole      & $0.1^\circ \times 0.1^\circ$ &   0E /   1E / 89N / 90N & 0   \\
    Equator   & $0.1^\circ \times 0.1^\circ$ &   0E /   1E /  0N / 1N  & 0   \\
    Global    & $ 10^\circ \times  10^\circ$ & 180W / 180E / 90S / 90N & 0   \\
    Satellite & $ 10^\circ \times  10^\circ$ & 180W / 180E / 90S / 90N & 260 \\
\end{tabular}
\end{table}

@@

\subsection{Sinusoidal Density}

@@

We will consider spherical shells with a sinusoidal density defined as follows:

\begin{equation}
    \rho(r') = A \sin \left( 2 \pi b \frac{r' - R}{T} \right) + A,
    \label{eq:density-sine}
\end{equation}

@@

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the $g_z$ of the spherical shells detailed in
Table~\ref{tab:shell-models} on each grid detailed in Table~\ref{tab:grids}.
Each shell is assigned with different sinusoidal density functions by changing the
values of $b$ in Eq.~\ref{eq:density-sine} (Fig.~\ref{fig:sine-densities}).
We fixed the distance-size ratio $D$ to the ones obtained for the linear density case
and explored values of $\delta$ ranging from $10^{-4}$ to $1$.
The analytical solution for the potential $V$ can be found on Appendix~\ref{sec:shell}.

Fig.~\ref{fig:sine-densities} shows the sinusoidal density functions assigned to every
spherical shell and Fig.~\ref{fig:delta-sine} shows the resulting relative differences
between the analytical and the numerical solutions.
In order to improve the visualization of the results, each curve corresponds to the
maximum difference between all shell models for the same value of $b$.

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/sine-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/sine-densities.pdf}
}
\caption{
    Sinusoidal density functions assigned to each spherical shell in the $\delta$ ratios
    determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-sine}.
}
\label{fig:sine-densities}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/sine-density-diffs.pdf}
\caption{
    Numerical error for different sinusoidal density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by the spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-sine}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the shell models detailed on Table~\ref{tab:shell-models} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case.
    Each curve corresponds to the maximum difference between every shell model with the
    same value of $b$.
    }
\label{fig:delta-exponential}
\end{figure*}
